At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information

### 2019-12-09 manuscript/supporting_info.tex
adjusted some sticky refs in the diff file, finished editing reply. Very tired of this whole enterprise

@@

\section*{Supporting information 4: Distributions of $p$-values for permuted networks}

@@

\section*{Supporting information 5: Details of within-family regressions}

>>>>

\section*{Supporting information 4: A test of connectance}

    To test whether the relationship between phylogenetic distance and niche overlap depended on connectance, we fit a general linear model for the slope of this relationship inferred from the glm models against connectance (C), network type (again using herbivory networks as a baseline), and their interaction:
    %
      \begin{equation}
        \beta_{distance} \propto \beta_{C} \eta_{N} + \beta_{pollination} I_N + \beta_{C:pollination} \eta_{N} I_N ,
      \end{equation}
    %
    where $\eta_{N}$ is the number of plant pairs in network $N$ for which distances could be calculated, $I_N$ is an indicator equal to 1 if network $N$ is a pollination network and 0 otherwise.

    The strength of the relationship did not depend on network type ($\beta_{pollination}$=-0.015, $p$=0.860), connectance ($\beta_{C}$=-0.652, $p$=0.051), or their interaction ($\beta_{C:pollination}$=0.687, $p$=0.084). 
    If we removed the interaction term and re-fit the model, the strength of the relationships between phylogenetic distance and niche overlap still did not depend on connectance ($\beta_{C}$=-0.169, $p$=0.356). We conclude that connectance does not constrain pairwise niche overlap in our dataset.

@@

\section*{Supporting information 5: Distributions of $p$-values for permuted networks}

@@

\section*{Supporting information 6: Details of within-family regressions}
